On Secure Delegation of SampBQP with a Classical Client

### 2020-03-30 qpip.tex
Add discussion notes

We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy.
We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
We present our protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.

@@

	Inputs:
	\begin{itemize}
		\item Error parameter $\varepsilon\in(0, 1)$
		\item Input string $x\in\set{0, 1}^n$
		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}.
		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}.
		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}.
	\end{itemize}

	Pseudocode:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies \Ethan{This isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is easy to see $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon^{-1})$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$

@@

	The first step of our analysis is to use de Finetti's theorem.
	Randomly picking $m+1$ out of $M$ registers is equivalent to first applying a random permutation to get some $\sigma'$ then taking the first $m+1$ registers.
	A random permutation, in turn, is a classical mix over all possible permutations:
	$$\sigma'=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\Pi\sigma\Pi^\dagger.$$
	It is simple to check that $\sigma'$ is permutation-invariant:
	fix $\tilde{\Pi}\in\Sym(M)$, then
	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger
	=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\tilde{\Pi}\Pi\sigma\Pi^\dagger\tilde{\Pi}^\dagger
	=\frac{1}{\abs{\Sym(M)}}\sum_{\hat{\Pi}\in\Sym(M)}\hat{\Pi}\sigma\hat{\Pi}^\dagger
	=\sigma'$$
	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$.

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	Note that the ground state has $\abs{A}=n+T+\frac{T}{e}$ qubits.
	That is, $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$ such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\ln\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$:
	$$J=\set{j\in I|p_j<\frac{1}{2}-2\kappa}$$

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$

	Now, for the other case, $j\notin J$, by \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$

	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $\poly(\varepsilon)$ due to the padding,
	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point.

	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
\end{prf}

>>>>

We start with a $\SampBQP$ problem $(D_x)_{x\in\set{0, 1}^*}$ and an input $x$,
then there exists some quantum circuit $C$ that samples from $D_x$ within desired accuracy. \Ethan{Define some kinda $\varepsilon_0$ for this}
We assume without loss of generality that $C$ comprises of only Hadamard and Toffoli gates.
We present our protocol that allows a client to verifiably obtain the measurement outcome of $C(x)$.

@@

	Inputs:
	\begin{itemize}
		\item Error parameter $\varepsilon\in(0, 1)$
		\item Input string $x\in\set{0, 1}^n$
		\item Quantum circuit $C$ of size $T$ consisting of only Hadamard and Toffoli gates \Ethan{move this into ingredients and put SampBQP instance as inputs}
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
		\item Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}. \Ethan{Also bring $H_C$ in. More descriptions. Make it more intuitive.}
		\item $\cVGS$ be the way to check said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix}
		\item Define $c\in\bbR$ as in \Cref{cor:HamCheck}. \Ethan{Just make sure it's less than 10 and write 10. Also it shouldn't be an ingredient if it's $c$}
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{20}}{\varepsilon^{32}}\ln(\frac{T}{\varepsilon})$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ \Ethan{TODO Define this} only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is easy to see $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) \Ethan{Theorem numbering needs fix} with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$

@@

	The first step of our analysis is to use de Finetti's theorem.
	Randomly picking $m+1$ out of $M$ registers is equivalent to first applying a random permutation then taking the first $m+1$ registers.
	A random permutation, in turn, is a classical mix over all possible permutations:
	$$\sigma'=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\Pi\sigma\Pi^\dagger.$$
	It is simple to check that $\sigma'$ is permutation-invariant:
	fix $\tilde{\Pi}\in\Sym(M)$, then
	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger
	=\frac{1}{\abs{\Sym(M)}}\sum_{\Pi\in\Sym(M)}\tilde{\Pi}\Pi\sigma\Pi^\dagger\tilde{\Pi}^\dagger
	=\frac{1}{\abs{\Sym(M)}}\sum_{\hat{\Pi}\in\Sym(M)}\hat{\Pi}\sigma\hat{\Pi}^\dagger
	=\sigma'$$
	where the second equality is by relabeling $\tilde{\Pi}\Pi=\hat{\Pi}$.

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	Note that the ground state has $\abs{A}=n+T+\frac{T}{\varepsilon}$ qubits.
	\Ethan{Think about notation... maybe $s$? typeof($A$) is strange. Also an error here.}
	That is, \Ethan{type out ``there exists" if in sentence} $\exists\rho=\sum_j w_j\rho_j^{\otimes m+1}$
	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
	such that for all quantum-classical channels $\Lambda_i$ on $\abs{A}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\ln\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

	\Ethan{In our context, lambda i is ground state check... etc. and rho 1 rho 2 are...}

	Now we separate the $\rho_j$ into two categories base on $p_j$, the accept probability of $\cVGS(\rho_j)$: \Ethan{Wording issue; make it obvious I'm defining $p_j$}
	$$J=\set{j\in\bbN|p_j<\frac{1}{2}-2\kappa}$$

	\Ethan{Definition of $J$ is extraneous; just cut into two cases.}

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	\Ethan{Delete the following and just say it's standard application of Chernoff bound}
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2\kappa$,
	then clearly $\Prob{Z\geq\frac{m}{2}-\kappa m}<\Prob{Y\geq\frac{m}{2}-\kappa m}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-\kappa m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1})$$
	where $\mu=mp_y=\frac{m}{2}-2\kappa m$ and $\delta=\frac{2\kappa}{1-4\kappa}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$

    \Ethan{Fix the kets}

	Now, for the other case, $j\notin J$, by \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$
	\Ethan{Trace distance notation}

	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $\poly(\varepsilon)$ due to the padding,
	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point. \Ethan{get rid of the remaining polys}

	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
	\Ethan{Be more careful here. Actually sum up errors.}
\end{prf}
